---
title: "Reproducible workflow"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

## Introduction

Please look the `README` file for further details on reproducing the results of this project. Note that the following chunks are supposed to run sequentially.

## Load libraries

Check that the [pacman](https://github.com/trinker/pacman) package is installed. Alternatively, note that you can use the [checkpoint](https://github.com/RevolutionAnalytics/checkpoint) package to build an environment identical to the date of completion of the present project. Look at the `Session information` tab below. After [pacman](https://github.com/trinker/pacman) is installed, the `p_load` function will check that the selected packages are installed. If they are, it will load them; if not, it will first install them and then load them.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=TRUE}
# if (!require(checkpoint)) install.packages('checkpoint')
# checkpoint::checkpoint("2021-11-18")

if (!require(pacman)) install.packages('pacman')

pacman::p_load(tidyverse,runjags,coda,ggmcmc,xtable,data.table,viridis,ggsci,patchwork,mvtnorm,truncnorm,grateful)

```

## Load utilities and functions

```{r, eval=FALSE}
source("code/utilities.R")
```

## Conduct the analyes

This will run the analyses in an order temporal sequence.

```{r, eval=FALSE}
# All periods ####

for(TimePeriod in c("PreBSE","BSE","PostBSE")){

  # Loada data: ####
  load_data(TimePeriod)

  # Find the equilibrium population and the variance of state variables: ####
  find_equilibrium_population(TimePeriod,
                              adapt = 10000,
                              burnin = 100000,
                              sample = 1000,
                              thin = 100)

  # Fit the SSSSDDDM: ####
  fit_S4D3M(TimePeriod,
               n.chains = 3,
               adapt = 10000,
               burnin = 500000,
               sample = 1000,
               thin = 500,
               mcmc_diagnostics_plots = TRUE,
               PPC_simulations = TRUE,
               N_PPC_Fits = 100,
               burnin_ppc = 100000,
               sample_ppc = 1000,
               thin_ppc = 100)

  }
```

## Produce the figures

The call to this function will produce all the figures in the paper

```{r, eval=FALSE}

Figures()

```


## Compile the manuscript

Once the analyses are completed and the figures produced, this shell call to the `Makefile` will compile and open the manuscript and related supplementary material: 

```{bash, eval=FALSE}
make compile
```

